The role of cross-linguistic lexical similarity on bilingual word acquisition

### 2021-09-15 Rmd/trajectories_manuscript.tex
mode report to Markdown

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,man,floatsintext]{apa6}
\usepackage{lmodern}
\usepackage{amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
  \usepackage{amssymb}
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={The role of cross-linguistic lexical similarity on bilingual word acquisition},
  pdfauthor={Gonzalo Garcia-Castro1, Daniela Avila-Varela1, \& Nuria Sebastian-Galles1},
  pdflang={en-EN},
  pdfkeywords={lexical acquisition, vocabulary, bilingualism},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\ifxetex
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[shorthands=off,main=english]{babel}
\fi
\ifluatex
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

Floccia et al.~pointed to \emph{parallel activation} as the main mechanism underpinning their results. The parallel activation hypothesis suggests that bilinguals activate both languages simultaneously during speech production or comprehension. This phenomenon is the result of the activation of lexical representations in both languages, even when only one is in use during production (Costa, Caramazza, \& Sebastian-Galles, 2000; Hoshino \& Kroll, 2008) or comprehension (Thierry \& Wu, 2007). One of the clearest examples of parallel activation was provided by Costa, Caramazza, and Sebastian-Galles (2000). In this study, Catalan-Spanish monolingual and bilingual adults were asked to name pictures of common objects in Spanish. In half of the trials, the object labels were cognates in Spanish and Catalan (\emph{árbol}-\emph{arbre}, translations of \emph{tree}), whereas in the other half of the trials labels were non-cognates (\emph{mesa}-\emph{taula}, translations of \emph{table}). Bilinguals named cognate pictures faster than non-cognate pictures, even after adjusting for the lexical frequency of the items. Importantly, Spanish monolinguals did not show this effect. These results suggest that, for the bilinguals, Catalan phonology was activated during the production of Spanish words, facilitating the naming of cognate pictures. Several recent studies have also provided similar evidence in comprehension in children (Poulin-Dubois, Bialystok, Blaye, Polonia, \& Yott, 2013; e.g., Von Holzen \& Mani, 2012). Parallel activation is therefore a plausible mechanism to account for Floccia et al.'s results: cognates increase the amount of activation in both languages, facilitating word acquisition. Therefore, children learning language pairs with a larger proportion of cognates are predicted to show larger vocabulary sizes. If cognates are the reason for this facilitation effect, it could be predicted that cognates are acquired earlier than non-cognates. Likely as it might seem, an earlier age of acquisition for cognates is not the only scenario where Floccia et al.'s results are account for.
For example, languages that share more cognates might also share a larger overlap in their phonemic inventories, which could facilitate the acquisition of all words, regardless of their cognate status.

@@

\hypertarget{references}{%
\subsection{References}\label{references}}

@@

\hypertarget{references-1}{%
\section{References}\label{references-1}}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\hypertarget{ref-bergelson2020comprehension}{}%
Bergelson, E. (2020). The comprehension boost in early word learning: Older infants are better learners. \emph{Child Development Perspectives}, \emph{14}(3), 142--149.

\leavevmode\hypertarget{ref-bergelson2012months}{}%
Bergelson, E., \& Swingley, D. (2012). At 6--9 months, human infants know the meanings of many common nouns. \emph{Proceedings of the National Academy of Sciences}, \emph{109}(9), 3253--3258.

\leavevmode\hypertarget{ref-bloom2002children}{}%
Bloom, P. (2002). \emph{How children learn the meanings of words}. MIT press.

\leavevmode\hypertarget{ref-bosch2014first}{}%
Bosch, L., \& Ramon-Casas, M. (2014). First translation equivalents in bilingual toddlers' expressive vocabulary: {Does} form similarity matter? \emph{International Journal of Behavioral Development}, \emph{38}(4), 317--322. \url{https://doi.org/10.1177/0165025414532559}

\leavevmode\hypertarget{ref-bosch2014first}{}%
Bosch, L., \& Ramon-Casas, M. (2014). First translation equivalents in bilingual toddlers' expressive vocabulary: {Does} form similarity matter? \emph{International Journal of Behavioral Development}, \emph{38}(4), 317--322. \url{https://doi.org/10.1177/0165025414532559}

\leavevmode\hypertarget{ref-braginsky2019consistency}{}%
Braginsky, M., Yurovsky, D., Marchman, V. A., \& Frank, M. C. (2019). Consistency and variability in children's word learning across languages. \emph{Open Mind}, \emph{3}, 52--67.

\leavevmode\hypertarget{ref-cattani2014much}{}%
Cattani, A., Abbot-Smith, K., Farag, R., Krott, A., Arreckx, F., Dennis, I., \& Floccia, C. (2014). How much exposure to english is necessary for a bilingual toddler to perform like a monolingual peer in language tests? \emph{International Journal of Language \& Communication Disorders}, \emph{49}(6), 649--671.

\leavevmode\hypertarget{ref-costa2000cognate}{}%
Costa, A., Caramazza, A., \& Sebastian-Galles, N. (2000). The {Cognate} {Facilitation} {Effect}: {Implications} for {Models} of {Lexical} {Access}. \emph{Journal of Experimental Psychology}, \emph{26}(5), 1283--1296. \url{https://doi.org/10.1037/0278-7393.26.5.1283}

\leavevmode\hypertarget{ref-costa2000cognate}{}%
Costa, A., Caramazza, A., \& Sebastian-Galles, N. (2000). The {Cognate} {Facilitation} {Effect}: {Implications} for {Models} of {Lexical} {Access}. \emph{Journal of Experimental Psychology}, \emph{26}(5), 1283--1296. \url{https://doi.org/10.1037/0278-7393.26.5.1283}

\leavevmode\hypertarget{ref-fabian2016investigating}{}%
Fabian, A. P. (2016). Investigating vocabulary abilities in bilingual portuguese-english-speaking children.

\leavevmode\hypertarget{ref-fenson1994variability}{}%
Fenson, L., Dale, P. S., Reznick, J. S., Bates, E., Thal, D. J., Pethick, S. J., \ldots{} Stiles, J. (1994). Variability in early communicative development. \emph{Monographs of the Society for Research in Child Development}, i--185.

\leavevmode\hypertarget{ref-fenson1994variability}{}%
Fenson, L., Dale, P. S., Reznick, J. S., Bates, E., Thal, D. J., Pethick, S. J., \ldots{} Stiles, J. (1994). Variability in early communicative development. \emph{Monographs of the Society for Research in Child Development}, i--185.

\leavevmode\hypertarget{ref-floccia2018introduction}{}%
Floccia, C., Sambrook, T. D., Delle Luche, C., Kwok, R., Goslin, J., White, L., \ldots{} others. (2018). I: INTRODUCTION. \emph{Monographs of the Society for Research in Child Development}, \emph{83}(1), 7--29.

\leavevmode\hypertarget{ref-gonzalez2020bilingual}{}%
Gonzalez-Barrero, A. M., Schott, E., \& Byers-Heinlein, K. (2020). Bilingual adjusted vocabulary: A developmentally-informed bilingual vocabulary measure.

\leavevmode\hypertarget{ref-hoff2012dual}{}%
Hoff, E., Core, C., Place, S., Rumiche, R., Señor, M., \& Parra, M. (2012). Dual language exposure and early bilingual development. \emph{Journal of Child Language}, \emph{39}(1), 1.

\leavevmode\hypertarget{ref-hoshino2008cognate}{}%
Hoshino, N., \& Kroll, J. F. (2008). Cognate effects in picture naming: Does cross-language activation survive a change of script? \emph{Cognition}, \emph{106}(1), 501--511.

\leavevmode\hypertarget{ref-jusczyk1995infants}{}%
Jusczyk, P. W., \& Aslin, R. N. (1995). Infants′ detection of the sound patterns of words in fluent speech. \emph{Cognitive Psychology}, \emph{29}(1), 1--23.

\leavevmode\hypertarget{ref-levenshtein1966binary}{}%
Levenshtein, V. I., \& others. (1966). Binary codes capable of correcting deletions, insertions, and reversals. In \emph{Soviet physics doklady} (Vol. 10, pp. 707--710). Soviet Union.

\leavevmode\hypertarget{ref-oller2002language}{}%
Oller, D. K., \& Eilers, R. E. (2002). \emph{Language and literacy in bilingual children} (Vol. 2). Multilingual Matters.

\leavevmode\hypertarget{ref-patterson2004comparing}{}%
Patterson, J. L. (2004). Comparing bilingual and monolingual toddlers' expressive vocabulary size.

\leavevmode\hypertarget{ref-patterson2004bilingual}{}%
Patterson, J., Pearson, B., \& Goldstein, B. (2004). Bilingual language development and disorders in spanish--english speakers.

\leavevmode\hypertarget{ref-pearson1994patterns}{}%
Pearson, B. Z., \& Fernández, S. C. (1994). Patterns of interaction in the lexical growth in two languages of bilingual infants and toddlers. \emph{Language Learning}, \emph{44}(4), 617--653.

\leavevmode\hypertarget{ref-pearson1993lexical}{}%
Pearson, B. Z., Fernández, S. C., \& Oller, D. K. (1993). Lexical development in bilingual infants and toddlers: Comparison to monolingual norms. \emph{Language Learning}, \emph{43}(1), 93--120.

\leavevmode\hypertarget{ref-petitto2001bilingual}{}%
Petitto, L. A., Katerelos, M., Levy, B. G., Gauna, K., Tétreault, K., \& Ferraro, V. (2001). Bilingual signed and spoken language acquisition from birth: Implications for the mechanisms underlying early bilingual language acquisition. \emph{Journal of Child Language}, \emph{28}(2), 453.

\leavevmode\hypertarget{ref-poulin2013lexical}{}%
Poulin-Dubois, D., Bialystok, E., Blaye, A., Polonia, A., \& Yott, J. (2013). Lexical access and vocabulary development in very young bilinguals. \emph{International Journal of Bilingualism}, \emph{17}(1), 57--70.

\leavevmode\hypertarget{ref-schelletter2002effect}{}%
Schelletter, C. (2002). The effect of form similarity on bilingual children's lexical development. \emph{Bilingualism: Language and Cognition}, \emph{5}(2), 93--107. \url{https://doi.org/10.1017/S1366728902000214}

\leavevmode\hypertarget{ref-smithson2014bilingualism}{}%
Smithson, L., Paradis, J., \& Nicoladis, E. (2014). Bilingualism and receptive vocabulary achievement: Could sociocultural context make a difference. \emph{Bilingualism: Language and Cognition}, \emph{17}(4), 810--821.

\leavevmode\hypertarget{ref-thierry2007brain}{}%
Thierry, G., \& Wu, Y. J. (2007). Brain potentials reveal unconscious translation during foreign-language comprehension. \emph{Proceedings of the National Academy of Sciences}, \emph{104}(30), 12530--12535.

\leavevmode\hypertarget{ref-thordardottir2006bilingual}{}%
Thordardottir, E., Rothenberg, A., Rivard, M.-E., \& Naves, R. (2006). Bilingual assessment: Can overall proficiency be estimated from separate measurement of two languages? \emph{Journal of Multilingual Communication Disorders}, \emph{4}(1), 1--21.

\leavevmode\hypertarget{ref-thordardottir2006bilingual}{}%
Thordardottir, E., Rothenberg, A., Rivard, M.-E., \& Naves, R. (2006). Bilingual assessment: Can overall proficiency be estimated from separate measurement of two languages? \emph{Journal of Multilingual Communication Disorders}, \emph{4}(1), 1--21.

\leavevmode\hypertarget{ref-tincoff1999some}{}%
Tincoff, R., \& Jusczyk, P. W. (1999). Some beginnings of word comprehension in 6-month-olds. \emph{Psychological Science}, \emph{10}(2), 172--175.

\leavevmode\hypertarget{ref-von2012language}{}%
Von Holzen, K., \& Mani, N. (2012). Language nonselective lexical access in bilingual toddlers. \emph{Journal of Experimental Child Psychology}, \emph{113}(4), 569--586.

\leavevmode\hypertarget{ref-von2012language}{}%
Von Holzen, K., \& Mani, N. (2012). Language nonselective lexical access in bilingual toddlers. \emph{Journal of Experimental Child Psychology}, \emph{113}(4), 569--586.

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  english,
  man,man,floatsintext]{apa6}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={The role of cross-linguistic lexical similarity on bilingual word acquisition},
  pdfauthor={Gonzalo Garcia-Castro1, Daniela Avila-Varela1, \& Nuria Sebastian-Galles1},
  pdflang={en-EN},
  pdfkeywords={lexical acquisition, vocabulary, bilingualism},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
% Make \paragraph and \subparagraph free-standing
\ifx\paragraph\undefined\else
  \let\oldparagraph\paragraph
  \renewcommand{\paragraph}[1]{\oldparagraph{#1}\mbox{}}
\fi
\ifx\subparagraph\undefined\else
  \let\oldsubparagraph\subparagraph
  \renewcommand{\subparagraph}[1]{\oldsubparagraph{#1}\mbox{}}
\fi
% Manuscript styling
\usepackage{upgreek}
\captionsetup{font=singlespacing,justification=justified}

@@

\linenumbers
\usepackage{csquotes}
\ifXeTeX
  % Load polyglossia as late as possible: uses bidi with RTL langages (e.g. Hebrew, Arabic)
  \usepackage{polyglossia}
  \setmainlanguage[]{english}
\else
  \usepackage[main=english]{babel}
% get rid of language-specific shorthands (see #6817):
\let\LanguageShortHands\languageshorthands
\def\languageshorthands#1{}
\fi
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1 \everypar{\setlength{\hangindent}{\cslhangindent}}\ignorespaces\fi
  % set entry spacing
  \ifnum #2 > 0
  \setlength{\parskip}{#2\baselineskip}
  \fi
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}

@@

Floccia et al.~pointed to \emph{parallel activation} as the main mechanism underpinning their results. The parallel activation hypothesis suggests that bilinguals activate both languages simultaneously during speech production or comprehension. This phenomenon is the result of the activation of lexical representations in both languages, even when only one is in use during production (Costa, Caramazza, \& Sebastian-Galles, 2000; Hoshino \& Kroll, 2008) or comprehension (Thierry \& Wu, 2007). One of the clearest examples of parallel activation was provided by Costa et al. (2000). In this study, Catalan-Spanish monolingual and bilingual adults were asked to name pictures of common objects in Spanish. In half of the trials, the object labels were cognates in Spanish and Catalan (\emph{árbol}-\emph{arbre}, translations of \emph{tree}), whereas in the other half of the trials labels were non-cognates (\emph{mesa}-\emph{taula}, translations of \emph{table}). Bilinguals named cognate pictures faster than non-cognate pictures, even after adjusting for the lexical frequency of the items. Importantly, Spanish monolinguals did not show this effect. These results suggest that, for the bilinguals, Catalan phonology was activated during the production of Spanish words, facilitating the naming of cognate pictures. Several recent studies have also provided similar evidence in comprehension in children (Poulin-Dubois, Bialystok, Blaye, Polonia, \& Yott, 2013; e.g., Von Holzen \& Mani, 2012). Parallel activation is therefore a plausible mechanism to account for Floccia et al.'s results: cognates increase the amount of activation in both languages, facilitating word acquisition. Therefore, children learning language pairs with a larger proportion of cognates are predicted to show larger vocabulary sizes. If cognates are the reason for this facilitation effect, it could be predicted that cognates are acquired earlier than non-cognates. Likely as it might seem, an earlier age of acquisition for cognates is not the only scenario where Floccia et al.'s results are account for.
For example, languages that share more cognates might also share a larger overlap in their phonemic inventories, which could facilitate the acquisition of all words, regardless of their cognate status.

@@

@@

\hypertarget{references}{%
\section{References}\label{references}}

@@

\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-bergelson2020comprehension}{}}%
Bergelson, E. (2020). The comprehension boost in early word learning: Older infants are better learners. \emph{Child Development Perspectives}, \emph{14}(3), 142--149.

\leavevmode\vadjust pre{\hypertarget{ref-bergelson2012months}{}}%
Bergelson, E., \& Swingley, D. (2012). At 6--9 months, human infants know the meanings of many common nouns. \emph{Proceedings of the National Academy of Sciences}, \emph{109}(9), 3253--3258.

\leavevmode\vadjust pre{\hypertarget{ref-bloom2002children}{}}%
Bloom, P. (2002). \emph{How children learn the meanings of words}. MIT press.

\leavevmode\vadjust pre{\hypertarget{ref-bosch2014first}{}}%
Bosch, L., \& Ramon-Casas, M. (2014). First translation equivalents in bilingual toddlers' expressive vocabulary: {Does} form similarity matter? \emph{International Journal of Behavioral Development}, \emph{38}(4), 317--322. \url{https://doi.org/10.1177/0165025414532559}

\leavevmode\vadjust pre{\hypertarget{ref-braginsky2019consistency}{}}%
Braginsky, M., Yurovsky, D., Marchman, V. A., \& Frank, M. C. (2019). Consistency and variability in children's word learning across languages. \emph{Open Mind}, \emph{3}, 52--67.

\leavevmode\vadjust pre{\hypertarget{ref-cattani2014much}{}}%
Cattani, A., Abbot-Smith, K., Farag, R., Krott, A., Arreckx, F., Dennis, I., \& Floccia, C. (2014). How much exposure to english is necessary for a bilingual toddler to perform like a monolingual peer in language tests? \emph{International Journal of Language \& Communication Disorders}, \emph{49}(6), 649--671.

\leavevmode\vadjust pre{\hypertarget{ref-costa2000cognate}{}}%
Costa, A., Caramazza, A., \& Sebastian-Galles, N. (2000). The {Cognate} {Facilitation} {Effect}: {Implications} for {Models} of {Lexical} {Access}. \emph{Journal of Experimental Psychology}, \emph{26}(5), 1283--1296. \url{https://doi.org/10.1037/0278-7393.26.5.1283}

\leavevmode\vadjust pre{\hypertarget{ref-fabian2016investigating}{}}%
Fabian, A. P. (2016). Investigating vocabulary abilities in bilingual portuguese-english-speaking children.

\leavevmode\vadjust pre{\hypertarget{ref-fenson1994variability}{}}%
Fenson, L., Dale, P. S., Reznick, J. S., Bates, E., Thal, D. J., Pethick, S. J., \ldots{} Stiles, J. (1994). Variability in early communicative development. \emph{Monographs of the Society for Research in Child Development}, i--185.

\leavevmode\vadjust pre{\hypertarget{ref-floccia2018introduction}{}}%
Floccia, C., Sambrook, T. D., Delle Luche, C., Kwok, R., Goslin, J., White, L., \ldots{} others. (2018). I: INTRODUCTION. \emph{Monographs of the Society for Research in Child Development}, \emph{83}(1), 7--29.

\leavevmode\vadjust pre{\hypertarget{ref-gonzalez2020bilingual}{}}%
Gonzalez-Barrero, A. M., Schott, E., \& Byers-Heinlein, K. (2020). Bilingual adjusted vocabulary: A developmentally-informed bilingual vocabulary measure.

\leavevmode\vadjust pre{\hypertarget{ref-hoff2012dual}{}}%
Hoff, E., Core, C., Place, S., Rumiche, R., Señor, M., \& Parra, M. (2012). Dual language exposure and early bilingual development. \emph{Journal of Child Language}, \emph{39}(1), 1.

\leavevmode\vadjust pre{\hypertarget{ref-hoshino2008cognate}{}}%
Hoshino, N., \& Kroll, J. F. (2008). Cognate effects in picture naming: Does cross-language activation survive a change of script? \emph{Cognition}, \emph{106}(1), 501--511.

\leavevmode\vadjust pre{\hypertarget{ref-jusczyk1995infants}{}}%
Jusczyk, P. W., \& Aslin, R. N. (1995). Infants′ detection of the sound patterns of words in fluent speech. \emph{Cognitive Psychology}, \emph{29}(1), 1--23.

\leavevmode\vadjust pre{\hypertarget{ref-levenshtein1966binary}{}}%
Levenshtein, V. I., \& others. (1966). Binary codes capable of correcting deletions, insertions, and reversals. In \emph{Soviet physics doklady} (Vol. 10, pp. 707--710). Soviet Union.

\leavevmode\vadjust pre{\hypertarget{ref-oller2002language}{}}%
Oller, D. K., \& Eilers, R. E. (2002). \emph{Language and literacy in bilingual children} (Vol. 2). Multilingual Matters.

\leavevmode\vadjust pre{\hypertarget{ref-patterson2004comparing}{}}%
Patterson, J. L. (2004). Comparing bilingual and monolingual toddlers' expressive vocabulary size.

\leavevmode\vadjust pre{\hypertarget{ref-patterson2004bilingual}{}}%
Patterson, J., Pearson, B., \& Goldstein, B. (2004). Bilingual language development and disorders in spanish--english speakers.

\leavevmode\vadjust pre{\hypertarget{ref-pearson1994patterns}{}}%
Pearson, B. Z., \& Fernández, S. C. (1994). Patterns of interaction in the lexical growth in two languages of bilingual infants and toddlers. \emph{Language Learning}, \emph{44}(4), 617--653.

\leavevmode\vadjust pre{\hypertarget{ref-pearson1993lexical}{}}%
Pearson, B. Z., Fernández, S. C., \& Oller, D. K. (1993). Lexical development in bilingual infants and toddlers: Comparison to monolingual norms. \emph{Language Learning}, \emph{43}(1), 93--120.

\leavevmode\vadjust pre{\hypertarget{ref-petitto2001bilingual}{}}%
Petitto, L. A., Katerelos, M., Levy, B. G., Gauna, K., Tétreault, K., \& Ferraro, V. (2001). Bilingual signed and spoken language acquisition from birth: Implications for the mechanisms underlying early bilingual language acquisition. \emph{Journal of Child Language}, \emph{28}(2), 453.

\leavevmode\vadjust pre{\hypertarget{ref-poulin2013lexical}{}}%
Poulin-Dubois, D., Bialystok, E., Blaye, A., Polonia, A., \& Yott, J. (2013). Lexical access and vocabulary development in very young bilinguals. \emph{International Journal of Bilingualism}, \emph{17}(1), 57--70.

\leavevmode\vadjust pre{\hypertarget{ref-schelletter2002effect}{}}%
Schelletter, C. (2002). The effect of form similarity on bilingual children's lexical development. \emph{Bilingualism: Language and Cognition}, \emph{5}(2), 93--107. \url{https://doi.org/10.1017/S1366728902000214}

\leavevmode\vadjust pre{\hypertarget{ref-smithson2014bilingualism}{}}%
Smithson, L., Paradis, J., \& Nicoladis, E. (2014). Bilingualism and receptive vocabulary achievement: Could sociocultural context make a difference. \emph{Bilingualism: Language and Cognition}, \emph{17}(4), 810--821.

\leavevmode\vadjust pre{\hypertarget{ref-thierry2007brain}{}}%
Thierry, G., \& Wu, Y. J. (2007). Brain potentials reveal unconscious translation during foreign-language comprehension. \emph{Proceedings of the National Academy of Sciences}, \emph{104}(30), 12530--12535.

\leavevmode\vadjust pre{\hypertarget{ref-thordardottir2006bilingual}{}}%
Thordardottir, E., Rothenberg, A., Rivard, M.-E., \& Naves, R. (2006). Bilingual assessment: Can overall proficiency be estimated from separate measurement of two languages? \emph{Journal of Multilingual Communication Disorders}, \emph{4}(1), 1--21.

\leavevmode\vadjust pre{\hypertarget{ref-tincoff1999some}{}}%
Tincoff, R., \& Jusczyk, P. W. (1999). Some beginnings of word comprehension in 6-month-olds. \emph{Psychological Science}, \emph{10}(2), 172--175.

\leavevmode\vadjust pre{\hypertarget{ref-von2012language}{}}%
Von Holzen, K., \& Mani, N. (2012). Language nonselective lexical access in bilingual toddlers. \emph{Journal of Experimental Child Psychology}, \emph{113}(4), 569--586.
